### 2016-01-28 mcmc.tex
typo
problems

\begin{problem}
Run the MCMC sampling of \probemname~\ref{prob:twod} to...HOGG
\end{problem}

>>>>

\begin{problem}\label{prob:tuning}
Run the MCMC sampling of \problemname~\ref{prob:twod} with the
covariant Gaussian density.
Give the proposal density $q(x'\given x)$ a diagonal variance
tensor that is $Q$ times the two-dimensional identity matrix.
Assess the acceptance fraction as a function of $Q$.
Find (very roughly) the value of $Q$ that gives an acceptance
fraction of about 0.25.
\end{problem}

\begin{problem}
Re-do \problemname~\ref{prob:tuning} but instead of trying to reach a
certain acceptance fraction, try to minimize the autocorrelation time.
What do you get as the best value of $Q$?
\end{problem}
